Constraining the High Density Nuclear Symmetry Energy with Pions

### 2020-05-05 MSU-thesis-estee.tex
Update experiment section

\graphicspath{{images/spacecharge/} {images/} {images/mccomparison/}  {images/dataAnalysis_2/} {images/dynamicrange/} {images/dataAnalysis/}}

@@

% If you want a dedication page, specify the text of the dedication here and uncomment the next command.
%
\dedication{This thesis is dedicated to someone.}
%

%User defined commands
\newcommand{\spirit}{S$\pi$RIT }
\newcommand{\tin}[2]{{}^{#1}\mathrm{Sn} + {}^{#2}\mathrm{Sn}}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}

\includeonly{
%chapters/ch_intro,
%chapters/ch_theory,
chapters/ch_experiment,
chapters/ch_data_analysis,
%chapters/ch_data_analysis_2,
%chapters/ch_results
}

@@

%\include{chapters/ch_intro}
%\include{chapters/ch_theory}
\include{chapters/ch_experiment}
\include{chapters/ch_data_analysis}
%\include{chapters/ch_data_analysis_2}
%\include{chapters/ch_results}

>>>>

\graphicspath{{images/spacecharge/} {images/} {images/mccomparison/}  {images/dataAnalysis_2/} {images/dynamicrange/} {images/dataAnalysis/} {images/experiment/} }

@@

% If you want a dedication page, specify the text of the dedication here and uncomment the next command.
%
\dedication{This thesis is dedicated to someone.}
%
%User defined commands
\newcommand{\spirit}{S$\pi$RIT }
\newcommand{\tin}[2]{{}^{#1}\mathrm{Sn} + {}^{#2}\mathrm{Sn}}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}

\DeclareSIUnit\torr{Torr}
\DeclareSIUnit\eVperc{\eV\per\clight}
\DeclareSIUnit\micron{\micro\metre}
\DeclareSIUnit\mrad{\milli\rad}
\DeclareSIUnit\gauss{G}

\includeonly{
%chapters/ch_intro,
%chapters/ch_theory,
chapters/ch_experiment,
%chapters/ch_data_analysis,
%chapters/ch_data_analysis_2,
%chapters/ch_results
}

@@

%\include{chapters/ch_intro}
%\include{chapters/ch_theory}
\include{chapters/ch_experiment}
%\include{chapters/ch_data_analysis}
%\include{chapters/ch_data_analysis_2}
%\include{chapters/ch_results}

### 2020-05-05 chapters/ch_data_analysis.tex
Update experiment section

Need to explain pedestal subtraction 
GG noise subtraction

@@

@@

\begin{table*}\centering
\ra{1.3}
\begin{tabular}{@{}rrrrcrrrcrrr@{}}\toprule
& \multicolumn{3}{c}{$100 MeV$} & \multicolumn{3}{c}{$100 MeV$} & \multicolumn{3}{c}{$300 MeV$}\\
\cmidrule{2-4} \cmidrule{6-8} \cmidrule{10-12}
& &\multicolumn{2}{c}{Measured} & & \multicolumn{2}{c}{Measured} & & \multicolumn{2}{c}{Measured}\\
\cmidrule{3-4} \cmidrule{7-8} \cmidrule{11-12}
Particle &\phantom{abc} & Measured & E$\times$B\\
\midrule
p   & 882.8 & 929.5 & 877.3 & 903.5 & 929.5 & 889 &\phantom{abcdef} & f & f \\
d   & 817.1 & 831.15 & d & 898.5 & e & e & 1621.1 & 1704 & 1612\\
t   & 589.5 & d & d & 887 & e & e & 1612.4 & f & f  \\
$^{3}$He  & 1617.3  & d & d & 1795.2 & e & e & 3236.4 & f & f\\
$^{4}$He  & 1405.6  & d & d & 1782.9 & e & e & 3226.4 & f & f \\
\bottomrule
\end{tabular}
\caption{Summary of expected cocktail. }
\label{tb:cocktailsummary}
\end{table*}

@@

While the goal of these tasks are to simulate important properties of a TPC, there are several effects which cannot be easily simulated. Several examples are biases due to triggering detectors (preferential selection of a reaction plane), saturation effects in the electronics, track multiplicity, and several other systematic sources common to all experiments. Simulating each issue individually would be impractical and time consuming, if not impossible. By embedding monte carlo tracks into experimental data -- and propagating through the tracking and reconstruction algorithm -- one can account for all sources these type of sources with a monte carlo type approach.

@@

As discussed in Section~\ref{sec:software}, the software is composed of several task, each which introduce errors through assumptions made in the tracking algorithm. The detector system itself introduces errors related to the physical measurement itself. By modeling the TPC, and its materials, the a Geant4 simulation provides an accurate description of interactions of a particles traversing the materials of the TPC.

% Evaluating the errors introduced by the software is the most straight forward exercise; let the software routine process an input and measure the result. Understanding the physical measurement requires modeling the physics involved in the theory and operations of TPCs and the electronics.

 % The experimental setup itself is quite large and complex, several ancillary detectors such as the Kyoto multiplicity array, Krakow veto array, Active veto array, beam identification detectors, etc. Even if a full accurate model could be constructed the complex trigger logic of the DAQ system would be impossible to model. If we notice that the biases and errors of the entire experimental setup is contained in the measured experimental data. Therefore, by inputting the MC data into a real experimental event (and measuring the output of that MC track) we can estimate the errors of the experimental setup. 
Before begging the detailed description of the embedding software, it is worth noting that the MC embedding was analyzed as a separate data set from the published data to avoid any issue of MC embedded tracks making it into the final published data.

The detailed flow diagram of the software implementation of embedding is shown in Fig.~\ref{fig:flow}.

@@

Once the MC simulation of a track response in the TPC is created, we directly embed the MC signals into data by superimposing the MC signals into the data time bucket spectrum, pad-by-pad. We will refer to this superimposed data as ``embedded data", only the MC signals as ``MC data", and data only containing the experimental signals as ``experimental data". The three set of data are each independently analyzed by the PSA algorithm, Section~\ref{sec:psa}, finding the hits in each data set. Part of the PSA task is to identify which hits in the embedded data are MC hits and which are from the original data. Once identified the embedded hits can be tagged and tracked through the entire software.

 By comparing the hits identified in the embedded set against the experimental data set we can first identify which embedded hits belong to the original experimental hit subset. For hits to match, they must satisfy two criteria; $\left|(Q_{\mathrm{Data}} - Q_{\mathrm{Embed} })/Q_{\mathrm{Data}}\right| < .05$ and $\left|t_{\mathrm{Embed} } - t_{\mathrm{Data} }\right| < 3$ where $Q$ and $t$ represent the charge and time of the hit respectively. We then remove these hits in the embedded data set which satisfy the conditions of experimental data hits.

The surviving hits are then compared with the MC hit data set, where the criteria for a matching MC hit is, $\left|t_{\mathrm{Embed} } - t_{\mathrm{MC} }\right| < 3$.  We do not require a matching criteria for the charge values since the pions we wish to study induce small signals relative to most of the particles producing signals in the experimental data as not to bias the charge values in the embedded data.  Since we removed almost all of the experimental hits in the first step, requiring only a time bucket cut in the second comparison is sufficient to tag the embedded MC hits. Each embedded hit that passes both criteria is tagged as an MC embedded hit. From here, the embedded data is treated as if it were real data passing through all the software algorithms as we use in the real data analysis. If a helix track has one hit that is embedded it will be tagged as embedded. Hits in a helix track are then clustered; if a cluster contains one embedded hit it is itself tagged as an embedded cluster. If a track that is reconstructed contains any embedded clusters, it is an embedded track.

The goal of this na\"ive tagging is to preserve all the information of where the embedded hits, clusters, and tracks have gone. The  job of the embedded correlation task is to identify which of the embedded tracks are candidates for the original input track. Several things may happen along the process of embedding. A track could break up, lose or share its charge with and adjacent track, or maybe not be identified for other reasons. For the embedded track to be a candidate it must satisfy two conditions, $N_{sat} > 5$ and $N_{\mathrm{sat}}/N_{\mathrm{Total}} \geq .5$, where $N_{\mathrm{sat}}$ is the number of saturated clusters in a track and $N_{\mathrm{Total}}$ is the number of total clusters. The first criteria is a simple minimum cut where to ensure there exists an embedded track and the second criteria is the strongest cut ensuring the track has at least half of its clusters coming from embedded MC signals. The set of tracks which satisfy both conditions are saved into an array of tracks which the user can use to study efficiency or track splitting.

In the case of efficiency analysis the user must select what they believe to be the track which most represents the original track. In this thesis, the track with the minimum distance to vertex is identified as the correct track. Though track splitting may occur, typically the split track has a distance to vertex which is very large and cut out from the analysis. The details of the efficiency analysis will be described later.

@@

>>>>

Need to explain pedestal subtraction

@@

\subsection{Gating grid noise subtraction}
The gating grid essentially is a fast switch which allows the charges of adjacent wires to reach equilibrium as fast as possible. In practice the impedance of both sides was not entirely matched properly and this caused an oscillating current to bounce back and forth in an under-dampened manner. This charge bouncing back and forth caused induced signals early in the time bucket spectrum which created and extra source of noise in the data. The ground grid shielded some of the noise, but since the path to ground was located at the ends of the TPC, the gating grid noise varied in intensity across the pads.

The gating grid itself was not always stable an only the ${}^{132}$Sn and ${}^{124}$Sn beams were relatively stable. Several times during the ${}^{108}$Sn and ${}^{112}$Sn beams the gating grid broke. After several data runs were taken, we took what is called gating grid noise runs to get the profile of the gating grid noise throughout the experiment. To achieve this the anode wires would be turned off and the trigger was allowed to otherwise operate normally, firing the gating grid to open as usual. Since the anode wires were all turned off no signals would be seen except those coming from the gating grid noise. Several thousand triggers of the gating grid were taken to get a good noise profile.

The average noise profile was constructed by averaging all the events in the gating grid runs, pad-by-pad; each pad had a slightly different noise profile since the impedance to each pad was slightly different. It is worth noting that the small electronics noise would be effectively canceled out by averaging over thousands of events. During the first stages of the software, the gating grid noise profile closest to that run would be subtracted from the raw data canceling the gating grid noise in that run.

@@

@@

While the goal of these tasks are to simulate important properties of a TPC, there are several effects which cannot be easily simulated. Several examples are biases due to triggering detectors (preferential selection of a reaction plane), saturation effects in the electronics, track multiplicity, and several other systematic sources common to all experiments. Simulating each issue individually would be impractical and time consuming, if not impossible. By embedding monte carlo tracks into experimental data -- and propagating through the tracking and reconstruction algorithm -- one can account for all sources with a monte carlo type approach.

@@

As discussed in Section~\ref{sec:software}, the software is composed of several tasks, each introduce biases through assumptions made in the tracking algorithm. The detector system introduces errors related to the physical measurement itself which can be addressed through modeling the TPC, and its materials. The biases involved in the the experimental set up are not always obvious but present in the experimental data. All three of these can be simultaneously addressed by embedding of MC tracks. Before beginning  the detailed description of the embedding software, it is worth noting that the MC embedding was analyzed as a separate data set from the published data to avoid any issue of MC embedded tracks making it into the final published data.

@@

The detailed flow diagram of the software implementation of embedding is shown in Fig.~\ref{fig:flow}. Once the MC simulation of a track response in the TPC is created, we directly embed the MC signals into data by superimposing the MC signals into the data time bucket spectrum, pad-by-pad. Figure~\ref{fig:mcevent} shows the response of a 200 MeV/c $\pi^-$ track in the TPC; we will embed this track into the data event, Fig.~\ref{fig:dataevent}, for an example. We will refer to experimental data containing embedded MC signals as ``embedded data", data only containing the MC signals as ``MC data", and data only containing only the experimental signals as ``experimental data". The three set of data are each independently analyzed by the PSA algorithm, Section~\ref{sec:psa},  which finds all the hits in each data set.

After this, the PSA algorithm contains the first and most important part of the embedding software. Here to the PSA task has the job to identify which hits in the embedded data are originally MC hits and which are from the original experimental data. Once identified, the embedded hits can be tagged and tracked through the entire software. By comparing the hits identified in the embedded set against the experimental data set we can first identify which embedded hits belong to the original experimental hit subset. For hits to match, they must satisfy two criteria, $\left|(Q_{\mathrm{Data}} - Q_{\mathrm{Embed} })/Q_{\mathrm{Data}}\right| < .05$ and $\left|t_{\mathrm{Embed} } - t_{\mathrm{Data} }\right| < 3$ where $Q$ and $t$ represent the charge and time of the hit respectively. We then remove these hits in the embedded data set which satisfy the conditions of experimental data hits.

The surviving hits are then compared with the MC hit data set, where the criteria for a matching MC hit is, $\left|t_{\mathrm{Embed} } - t_{\mathrm{MC} }\right| < 3$.  We do not require a matching criteria for the charge values since as not to bias the charge values selected as identified MC hits.  This is only accomplished by first removing almost all of the experimental hits in the first step. Each embedded hit that passes this criteria is tagged as an MC embedded hit. From here, the embedded data is treated as if it were real data passing through the same software analysis.

The goal of this na\"ive tagging is to preserve all the information of where the embedded hits, clusters, and tracks have gone. If a helix track has one hit that is embedded it will be tagged as embedded. When the hits in a helix track are clustered, if a cluster contains one embedded hit it is itself tagged as an embedded cluster. Furthermore, if a track that is reconstructed contains any embedded clusters, it is an embedded track.  It is the job of the embedded correlation task is to identify which of the final embedded tracks are candidates for the original input track. Several things may happen along the process of embedding. A track could break up, lose or share its charge with and adjacent track, or maybe not be identified at all for a variety of other reasons. For the embedded track to be a candidate of the input MC track, it must satisfy two conditions, $N_{sat} > 5$ and $N_{\mathrm{sat}}/N_{\mathrm{Total}} \geq .5$, where $N_{\mathrm{sat}}$ is the number of saturated clusters in a track and $N_{\mathrm{Total}}$ is the number of total clusters. The first criteria is a simple minimum cut where to ensure there exists an embedded track. The second criteria is the strongest cut ensuring the track has at least half of its clusters coming from embedded MC signals. The set of tracks which satisfy both conditions are saved into an array of tracks which the user can use to study efficiency or track splitting.

In the case of efficiency analysis the user must select what they believe to be the track which most represents the original track. In this thesis, the track with the minimum distance to vertex is identified as the correct track. This is to get rid of the situation of track splitting where typically the split track has a distance to vertex which is very large and cut out from the analysis. The details of how the embedding is used to calculate the efficiency will be described later.

@@

The arrival time of signals originating from each pad may differ due to timing delays in the electronics and cabling. The timing differences will affect the y-position measurement of each track. The y-residuals reveal that the timing differences correspond to about $\pm$\SI{2}{\milli\metre} in position differences. The timing difference is stable for each pad across several runs. Figure~\ref{fig:coboCorr} shows the y-residuals, across all the rows , for three different layers. Before the correction one can see large deviations in the y-residuals which correspond to timing differences. The mean value of the y-residual distribution is fitted and a map is constructed for each pad. The data is then reconstructed subtracting the value of that map, $dy$, for each pad. The resulting corrected distribution is shown in Fig.~\ref{fig:coboCorr} for the same layer set. Figure~\ref{fig:yoff} also show the summary of all the pads before the correction and after the correction. There is a significant improvement in the width of the distribution going from \SI{1.5}{\milli\metre} to \SI{0.6}{\milli\metre}.

\begin{figure}[!htb]
  \begin{center}
    \includegraphics[width=0.33\textwidth]{before_row_at_layer10_yoffset.pdf}
    \includegraphics[width=0.33\textwidth]{before_row_at_layer30_yoffset.pdf}
    \includegraphics[width=0.33\textwidth]{before_row_at_layer50_yoffset.pdf}

    \includegraphics[width=0.33\textwidth]{after_row_at_layer10_yoffset.pdf}
    \includegraphics[width=0.33\textwidth]{after_row_at_layer30_yoffset.pdf}
    \includegraphics[width=0.33\textwidth]{after_row_at_layer50_yoffset.pdf}

    \caption{TBW\label{TBD}}
  \end{center}
  \label{fig:coboCorr}
\end{figure}

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{before_layer_yoffset.pdf}
        \caption{Y-offset for all layers before correction.} \label{fig:yoff_beforeLayer}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{after_layer_yoffset.pdf} 
        \caption{Y-offset for all layers after correction.} \label{fig:yoff_afterLayer}
    \end{subfigure}
     \hfill
    \begin{subfigure}[t]{.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{before_all_yoffset.pdf} 
        \caption{Distribution for all pads before correction.} \label{fig:yoff_allBefore}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{after_all_yoffset.pdf} 
        \caption{Distribution for all pads after correction.} \label{fig:yoff_allAfter}
    \end{subfigure}
    \caption{ }
\label{fig:yoff}
\end{figure}

### 2020-05-05 chapters/ch_experiment.tex
Update experiment section

\section{S$\pi$RIT TPC Overview}
Add Overview image with labels

The Samurai Pion-Reconstruction and Ion Tracker Time Projection Chamber (S$\pi$RI TPC) is a Multi-Wire Proportional Counter developed to measure pions and other light charge particles resulting from radioactive heavy ion collisions in a fixed target experiments.  The TPC is enclosed in a thin aluminum sheet walls all around in order to minimize neutron scattering and to allow for light charged particles to reach the arrays of scintillating bars detectors on the sides and downstream of the TPC. The S$\pi$RI TPC was developed to fit inside the Samurai dipole magnet used at the Rare Isotope Beam Factory (RIBF) at RIKEN in Wako-shi, Japan \cite{riken}; the dipole gap limited the vertical space of the TPC. More detail and specifications of the Samurai dipole magnet are given in \cite{samurai}.

@@

\subsection{Enclosure}

\subsection{Voltage Step Down}

@@

The field cage was designed to hang from the top plate and therefore needed to be of a lightweight construction. Also the materials needed to be thin to allow for light charged particle and neutrons to pass through without significant scattering for ancillary detectors. Therefore instead of a downstream wall, a large thin exit window was constructed. The cathode was constructed of an aluminum honeycomb laminate. Two sheets of ??? aluminum were bonded to a core of aluminum honeycomb structure providing a lightweight yet rigid structure for the cathode.

\begin{figure}[H]
\includegraphics[width=\linewidth]{fc_explode}
\caption{Exploded view of the S$\pi$RIT TPC}
\label{fig:fc_explode}
\end{figure}

The field cage was constructed from several panels of printed circuit boards (PCBs). The epoxy in the common PCB substrate FR4 contains bromine which is not suitable for the long term operation of a TPC, as the bromine will eventually cause gain reduction of the wires [CITE]. The halogen free material chosen was Rodgers ????. We built the TPC with the option to run explosive gases such  hydrogen, thus we decided to have field cage an isolated volume from the rest of the TPC enclosure. While the risk of a high voltage spark was minimized using the voltage step down, the risk of sparking when using an explosive gas could be further minimized by isolating the detector volume from the enclosure volume thereby allowing you to run an insulating gas between the field cage while running the explosive gas inside the detector volume only.

@@

\subsection{Voltage Step Down}

To lower the risk of a high voltage spark around the cathode region a voltage step down was developed. A series of 7 concentric copper rings with 20 MOhm resistors between them steps the cathode voltage down to ground. This minimizes sharp transitions of the electric field and therefore sparking.

\subsection{Wire Planes}
Add figure of gating grid transparency closed and open configuration

@@

@@

\subsection{Gas Properties}

\begin{equation}
\frac{d\vec{x}}{dt} = \frac{\mu}{1+(\omega\tau)^2}\Big(\vec{E} + \omega\tau\frac{\vec{E}\times\vec{B}}{|\vec{B}|}+\omega^2\tau^2\frac{\vec{E}\cdot\vec{B}}{|\vec{B}|^2}\vec{B}\Big)
\label{eq:elecdrift}
\end{equation}

@@

\begin{figure}
\includegraphics[width=\linewidth]{gain.png}
\caption{Number of electrons produced in a single avalanche on an anode wire. Two different voltages were simulated using Garfield++ at 1470 $V$ and 1214 $V$. The expected Polya distribution fit is also given in yellow.}
\label{fig:anodegain}
\end{figure}

@@

Add table for gas diffusion

\section{Ancillary Detectors }
\subsection{Kyoto Multiplicity Trigger}
\subsection{Krakow ?????? (KATANA)}

>>>>

\section{S$\pi$RIT TPC Overview}
%Add Overview image with labels
The Samurai Pion-Reconstruction and Ion Tracker Time Projection Chamber (S$\pi$RI TPC) is a Multi-Wire Proportional Counter developed to measure pions and other light charge particles resulting from radioactive heavy ion collisions in a fixed target experiments.  The TPC is enclosed in a thin aluminum sheet walls all around in order to minimize neutron scattering and to allow for light charged particles to reach the arrays of scintillating bars detectors on the sides and downstream of the TPC. The S$\pi$RI TPC was developed to fit inside the Samurai dipole magnet used at the Rare Isotope Beam Factory (RIBF) at RIKEN in Wako-shi, Japan \cite{riken}; the dipole gap limited the vertical space of the TPC. More detail and specifications of the Samurai dipole magnet are given in \cite{samurai}.

@@

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{exploded.png}
\caption{Overview of the \spirit TPC}
\label{fig:tpcExplode}
\end{figure}

\subsection{Enclosure}
The skeleton of the enclosure is composed of a rigid aluminum angle-iron frame. All walls are constructed of a aluminum frame with think sheet metal. All materials were made to be as thin to allow charged particles and neutrons to exit the TPC without scattering too much. This allows for a trigger to be created by placing detectors on the sides and downstream of the TPC. The enclosure itself is made to be gas tight with respects to the outside and the field cage. This is to allow for the possibility to run a different gas inside the enclosure than the field cage. Although, in this set of experiments we ran the same gas in the field cage and enclosure volume.

\subsection{Voltage Step Down}
The gap between the field cage's cathode and the ground of the enclosure is quite small. To prevent electric breakdown in the gas between this gap a series of concentric copper rings safely stepped down the voltage to ground; where each ring was separated by a resistor. There were 7 concentric rings with a \SI{10}{\mega\ohm} resistors in between, creating a resistor chain which steps down the voltage each ring by approximately \SI{1000}{\volt}.

@@

The field cage holds the detector gas and sets up a uniform electric field in which electrons can drift upwards toward the anode wires. It was designed to hang from the top plate and therefore needed to be of a lightweight construction. Also the materials needed to be thin to allow for light charged particle and neutrons to pass through without significant scattering for ancillary detectors. Therefore instead of a downstream wall, a large thin exit window was constructed. The cathode was constructed of an aluminum honeycomb laminate. Two sheets of ??? aluminum were bonded to a core of aluminum honeycomb structure providing a lightweight yet rigid structure for the cathode.

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{fc_overview.pdf}
\label{fig:fc_overview}
\caption{FC overview}
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{fc_overview2.pdf}
\label{fig:fc_overview2}
\caption{FC overview 2}
\end{figure}

The field cage was constructed from several panels of printed circuit boards (PCBs). The epoxy in the common PCB substrate FR4 contains bromine which is not suitable for the long term operation of a TPC, as the bromine will eventually cause gain reduction of the wires [CITE]. The halogen free material chosen was Cryogenic-G10. We built the TPC with the option to run explosive gases such hydrogen, thus we decided to have field cage an isolated volume from the rest of the TPC enclosure. While the risk of a high voltage spark was minimized using the voltage step down, the risk of sparking when using an explosive gas could be further minimized by isolating the detector volume from the enclosure volume thereby allowing you to run an insulating gas between the field cage while running the explosive gas inside the detector volume only.

@@

\begin{equation}
V_n = V_{cath} \frac{R_p + (50 - n)R}{49\cdot R + R_p}
\label{eq:FCstrip}
\end{equation}

\begin{equation}
R_p = 49 \cdot R  \left(\frac{ y_{g.g.} - y_{cath} }{ y_{TP} - y_{cath} \frac{V_{cath} - V_{gg}}{V_{cath}} }- 1 \right)
\label{eq:TP_resistor}
\end{equation}

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{FC_schematic.pdf}
\label{fig:FC_schematic}
\caption{Schematic of the electric connections relevant to the Field Cage system.}
\end{figure}
\subsection{Voltage Step Down}

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{TPC_schematic.pdf}
\caption{Schematic of the TPC system}
\label{fig:TPC_schematic}
\end{figure}

Figure~\ref{fig:FC_schematic} shows a cartoon drawing of the electrode geometry of the field cage walls. The basic idea of the field cage is to set up a constant electric field in the field cage volume to allow for a constant drift, in the presence of gas, for electrons. To accomplish this the field cage is composed of a set of copper strips which are set at a defined voltage by a resistor chain for a fixed distance between strips; setting up a constant electric field.

The cathode itself is connected to the HV supply through a \SI{10}{\mega\ohm} resistor and has an effective capacitance to ground of \SI{4}{\nano\farad}, $C_{VSD}$. The field cage is made of 50 inside copper strips and 49 outside copper strips; the strip thickness is exaggerated in the figure to show the detail. The first inside strip is connected to the cathode which is connected by an effective \SI{5}{\mega\ohm} resistor, $R$, to the next inside strip and the first outside strip. The resistor chain creates a voltage divider in which each strip is separated by a constant difference voltage at a fixed distance setting up a constant electric field. The last strip of the field cage is composed of partially a small inner strip on the PCB board and the aluminum top perimeter piece which holds the field cage together with the top plate of the TPC. Together their thickness is equal to the \SI{6}{\milli\metre} strip width of the other strips. The top perimeter is connected to electrical ground through a \SI{20}{\mega\ohm} resistor with the option to place an additional resistor in parallel to tune the voltage of the top perimeter.

@@

\subsection{Wire Planes}
%Add figure of gating grid transparency closed and open configuration 
There are three wire planes that sit underneath the pad-plane. The wire plane closest to the pad-plane (\SI{4}{\milli\metre}), is the anode wire. The next plane (\SI{12}{\milli\metre}), is the ground plane or frisch grid, and the last plane (\SI{14}{\milli\metre}), is the gating grid. The gating grid is the first plane that electrons meet as they drift upward towards the anode plane. The gating grid is operated as a gate either allowing electrons and ions through or blocking them entirely. The ground plane shields the inside volume of the TPC from the high voltages of the anode wires where the avalanche process of the electron takes place.

The ground plane is the least interesting plane and is shorted to the enclosure ground by a BNC terminator on the outside of the TPC. If we would like to calibrate the electronics of the TPC we typically inject a pulser into one end of the ground plane and terminate the other end with a \SI{50}{\ohm} termination.

In the open configuration the gating grid is transparent to electrons coming from the TPC volume and also allows for ions to move from the avalanche region into the TPC volume. It functions as the gate of the TPC where we only open the gating grid when an event meets the selection trigger criteria; minimizing the excessive exposure to the un-reacted beams which would quickly build up enormous amounts of space charge. We close the TPC after reading out approximately one TPC volume -- about \SI{10}{\micro\second}  -- of space to prevent the back-flow of ions from the avalanche region of that event. Since ions move with a velocity much slower than that of elections, the ions only move several \si{\micro\metre} in the time the gate is open; this allows for electrons to pass through while preventing the back-flow of ions into the FC volume. Figure~\ref{fig:gg_onoff} shows a Garfield simulation of the gating grid in both the on and off configurations. In the on configuration, all the wires share the same average voltage, $V_{g.g.}$, which is optimized for the case of 100\% electron transparency. In the off configuration the reference voltage $V_{g.g.}$ remains the same, but alternating wires get an offset voltage of $\pm \Delta V$, so that the electric field between wires is great enough to block incoming electrons; opening the grid from this closed bi-polar mode is simply done by removing the offset voltage and allowing the two wires to connect and equilibrate their charges back to the reference voltage.

\begin{figure}
\includegraphics[width=\textwidth]{wires_open.pdf}
\caption{Cartoon graphic of the wire plane structures}
\label{fig:wires_open}
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{gg_onoff.pdf}
\caption{On and off configurations of the gating grid.}
\label{fig:gg_onoff}
\end{figure}

The anode wires are typically biased to \SI{e3}{\volt} and are very thin, about \SI{20}{\micro\metre} in diameter. This creates a very high electric field very close to the anode wire in which the electron gains significant kinetic energy producing electrons until it terminates on the anode wire. The amount of electrons it produces depends on the anode wire voltage and the gas properties. The absolute gas gain was not experimentally measured but was simulated by a Garfield simulation. During the experiment the anode wires were biased to two different voltages. We will refer to the voltage \SI{1460}{\volt} as the ``high voltage" and \SI{1214}{\volt} as the ``low voltage". Only two sections were biased with the lower voltage setting due to concerns of a high current issue. Figure~\ref{fig:anodegain} shows the expected number of electrons distributions for electrons produced in a avalanche process of an electron creating a single avalanche. The distribution follows a Polya distribution as expected and the MC data in the simulation was fit with a Polya function \cite{blumrol}.

\begin{figure}[!htb]
\includegraphics[width=\linewidth]{gain.png}
\caption{Number of electrons produced in a single avalanche on an anode wire. Two different voltages were simulated using Garfield++ at 1470 $V$ and 1214 $V$. The expected Polya distribution fit is also given in yellow.}
\label{fig:anodegain}
\end{figure}

@@

\subsection{Gas Properties}
The gas used inside of the field cage was a mixture of 90\% Ar and 10\% Methane ($\mathrm{CH_4}$) by volume --so called P10--  gas, operated just under atmospheric pressure (1 atm). The  gas was continually flowed through the field cage and exited into the enclosure volume, finally passing through a bubbler to atmosphere. The gas purity was monitored with an oxygen and water monitor which are the two most concerning contaminants. The water never exceed  ??? ppm  and the oxygen level never exceeded ??? ppm. Figure~\ref{fig:driftvel} shows the drift velocity of P10 gas at 1 atm as a function of electric field value in \si{\volt\per\centi\metre}. Operating near the peak value of the drift velocity curve minimizes the change in the drift velocity as the effective field slightly changes due to slight variations in the pressure. The electric field in the experiment was \SI{125}{\volt\per\centi\per\metre} at \SI{760}{\torr}, giving a reduced electric field \SI{0.17}{\volt\per\centi\metre\per\torr}.

@@

The general formula for the drift velocity, $d\vec{x}/dt$, of an electron in the presence of electric and magnetic fields, $\vec{E}$ and $\vec{B}$, can be expressed in the Langevin equation as,

\begin{equation}
\frac{d\vec{x}}{dt} = \frac{\mu}{1+(\omega\tau)^2}\Big(\vec{E} + \omega\tau\frac{\vec{E}\times\vec{B}}{|\vec{B}|}+\omega^2\tau^2\frac{\vec{E}\cdot\vec{B}}{|\vec{B}|^2}\vec{B}\Big),
\label{eq:elecdrift}
\end{equation}

where $\mu$ is the signed drift velocity, $\omega$ is the cyclotron frequency, and $\tau$ is the collision parameter for a particular gas \cite{blumrol}.

Several properties of the gas were also simulated in Garfield such as the longitudinal and transverse diffusion, $sigma_l$ and $sigma_t$ respectively, and the electron and ion drift velocities, $v_d$ and $v_i$ respectively for the experimental electric field of \SI{125}{\volt\per\centi\metre}; summarized in Table~\ref{tb:gasprop}.

@@

%Add table for gas diffusion

\section{Ancillary Detectors }

\subsection{Kyoto Multiplicity Trigger}
%kyoto array sets multiplicity trigger
%scintillator bars

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{kyotoarray}
\label{fig:kyoto}
\caption{Kyoto array overview}
\end{figure}

\subsection{Krakow ?????? (KATANA)}
%beam veto
%beam trigger optional

\subsection{Active Veto Array}
